\chapter{Conclusion}
\label{chapter5}

During the development of this project, a series of discoveries were made about the currently available mobile test automation tools that support iOS. First, it came to realization that there are a lot of variables to consider when choosing a test automation framework. However, one can start by selecting the right type of test automation framework to work with given the characteristics of the project and the expertise of the team that will perform the test automation. Second, actually understanding the different elements, interactions and functionality a mobile application utilizes is key when working on test automation. Therefore, a detailed research on the pieces that are involved in a test automation tool was made. This produced a list of GUI components, gestures, testing capabilities, framework characteristics and features. Finally, the developed case study allowed the examination of the previously mentioned lists over the Firefox App providing real world examples of automated tests for some of the evaluated tools. Reading the code and watching the test execute in real time considerably contributes to the understanding of the test automation environment via a practical approach.

\section{Limitations}
	\begin{itemize}
		\item Limited options for iOS open source apps.
		\item Time scope of the project was not enough to actually develop the case study with third party and all-in-one test automation tools.
		\item All-in-one tools can be very expensive. For example, TestComplete will easily cost more than 6,000 USD a year with no add-ons.
	\end{itemize}


\section{Future work}

This project has several opportunities for improvement:

	\begin{itemize}
		\item Performing the same case study content with more test automation tools. 
		\item Making use of more iOS applications in order to reference more real world test cases and automated test scripts.
		\item Expanding the coverage tables, including more GUI components, gestures and testing capabilities for the used tools.
	\end{itemize}

